AIR4children: Artificial Intelligence and Robotics for Children

### 2021-01-31 article/tex/submission.tex
adds description of sections

\section{Open Source AI and Robotics}
The spirit of open source software since 19XX with the contributions 
of users of different skills made a culture of openly share code to make
more robust tools (i.e. firefox, ubuntu, etc). Much recently, something 
similar to software is happening for hardware. One example is the community 
for arduino that open-sourced diagrams, code and with a low-cost microcontroller
magaged to make wordwile impact.

@@

\subsection{Open Source AI}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

\subsection{Open Source Robotics}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

\section{Open AIR4Children}
The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

@@

\begin{table}
  \caption{Open source projects}
  \label{tab:freq}
  \begin{tabular}{ccl}
    \toprule
    Project name& Year of creation & Community\\
    \midrule
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 & - \\
    JPL Open Source Rover \cite{OSR:2018} & April 2018 & - \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 & 50K used robots in >70 countries\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

\subsection{Open hardware and software}
The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

@@

\subsection{Open teaching materials}

Serholt 2017 performed studies to quantify the social intereaction 
between robots and children (i.e., gaze, verbal interaction, gestures, 
and facial expressions). However robotics tutors are not yet to the point 
to deal with complex child-robot interactions. 
\cite{Serholt:2017}
A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Conclusions and future work}

The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.

>>>>

\section{Open Source AI and Robotics}
The spirit of open source software since 19XX with the contributions 
of users of different skills made a culture of openly share code to make
more robust tools (i.e. firefox, ubuntu, etc). Much recently, something 
similar to software is happening for hardware. One example is the community 
for arduino that open-sourced diagrams, code and with a low-cost microcontroller
magaged to make wordwile impact. See ~\ref{tab:opensourceprojects}.

@@

\subsection{Open Source AI}
[Section to describe open-source AI projects and related them to air4children].
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

\subsection{Open Source Robotics}
[Section to describe open-source robotics projects and related them to air4children.]
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

\section{Open AIR4Children}
[Section to describe the proposed project of air4children and the integration 
of opensource tools.]
The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
high-quality tables.

@@

\begin{table}
  \caption{Open source projects}
  \label{tab:opensourceprojects}
  \begin{tabular}{ccl}
    \toprule
    Project name& Year of creation & Community\\
    \midrule
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019 & - \\
    JPL Open Source Rover \cite{OSR:2018} & April 2018 & - \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 & 50K used robots in >70 countries\\
    $\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
  \bottomrule
\end{tabular}
\end{table}

\subsection{Open hardware and software}
[Section to describe the hardware and software that can be used in 
air4children.]
The ``\verb|figure|'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown
in the example below.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{sample-franklin}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

@@

\subsection{Open teaching materials}
[Section to describe open teaching materials, perhaps using non-traditional education systems.]
Serholt 2017 performed studies to quantify the social intereaction 
between robots and children (i.e., gaze, verbal interaction, gestures, 
and facial expressions). However robotics tutors are not yet to the point 
to deal with complex child-robot interactions. 
\cite{Serholt:2017}
A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before
the body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\verb|\maketitle| command:
\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\section{Conclusions and future work}
[for conclusions and future work].
The use of \BibTeX\ for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials
(``D. E. Knuth'') --- and the salient identifying features of a
reference should be included: title, year, volume, number, pages,
article DOI, etc.
